### 2020-06-30 TCS_version/09-appendix.tex
appendice Cxt_1

\lemmastruct*
\begin{proof}
  We prove the two items separately:
  \begin{enumerate}
\item by Definition~\ref{def:trans}, all the names that appear in the prefixes of any subprocess are in the set $\mathit{names}$ and thus restricted. 
They include all the reaction names $r_j$, all the production names $p_j$, all the entity names $s_i,s_o$, in all their decorated versions, and the name $\mathit{cxt}$. 
Therefore the chain $\upsilon$ must start and end with a $\silent$ action and cannot contain virtual links.
The only prefix that starts with $\silent$ is the one of the recursive init process $I$ (prefix $\link{\silent}{r_1}$) and the only prefixes that end with $\silent$ are those associated to reaction $a_u$ (as we have assumed that $p_{u+1} = \silent$, where $u$ is the number of reactions).
Then each prefix that starts with $r_j$ involves $p_j$ and $r_{j+1}$.
Thus all the prefixes associated with reactions must be concatenated and also the prefix associated with the context (remember that $r_{u+1} = \mathit{cxt}$), forming the backbone of the label.
Since the context processes is involved, then all entities processes are also involved.
Then, all the processes $I$, $P_a$, $P_s$ (or $\overline{P_s}$), and $\mathit{Cxt}$  must participate to each transition.
 \item for each reaction $aj \in A$, the c\CNA \ code of  $P_{aj}$ leaves one virtual link between two solid links of the types $\link{r_j}{\dots} \chainedlink{s_{i}}{\noact}\chainedlink{\noact}{s_{o}}\link{}{\dots}\link{}{r_{j+1}} {\dots}\link{p_j}{\dots}\link{}{p_{j+1}}$. Then, it derives that the process $P_{s}$, encoding the behaviour of entity $s$, can participate by filling the virtual link in the above transition by only offering one solid link of the form $\link{s_{i}}{s_{o}}$. In fact, there is no other way to generate a solid chain from $s_{i}$ to $s_{o}$.
 The same reasoning holds for the processes $\mathit{Cxt}$ and for all the decorated versions of $s_i,s_o$.
% $P_{s_1}$ can not participate with a link chain, as by juxtaposing  $\link{s_{1i}}{s_{1o}}$, not valid
 %link chains would be generated.
   \end{enumerate}
  \end{proof}

@@

 %\begin{proposition}(correctness 1)\\
 %\label{lem:struct}
%  Let ${\cal A} = (S, A)$ be a rs, and let  $\pi=(\gamma,\delta)$ be a $n$-step interactive process in $A$, with
% $\gamma = C_0,\dots,C_n$ and $\delta = D_0,\dots,D_n$.
%% We define $\pi' = (\gamma',\delta')$ with $\gamma' = C_0',\dots,C_{n-1}'$ and $\delta' = D_0',\dots,D_{n-1}'$ as $C_0' = C_1 \cup D_1$,  and
%% $C_i' = C_{i+1}$, $D_{i}' = D_{i+1}$ with $ 1 \leq i < n$.
%  Let   $P=[|{\cal A},\gamma|]$ be  its c\CNA~translation, and let $P'$ be such that $P \xrightarrow{\link{\silent}{\silent}}P'$.% then $P' = [|{\cal A},\gamma' |]$. 
%Then it holds that\\
% $P= \restrict{reacts,ctxs,ents} (\Pi_{a \in A}P_a| \Pi_{s \in S}CXT_s | \Pi_{s \in C_0}P_s| \Pi_{s \notin C_0}\overline{P}_s)$\\
% $P'= \restrict{reacts,ctxs,ents} (\Pi_{a \in A}P_a| \Pi_{s \in S}CXT_s | \Pi_{s \in C_1 \cup D_1}P_s| \Pi_{s \notin C_1 \cup D_1}\overline{P}_s)$
 %\end{proposition}
 \begin{proof}
 First, we note that all the channels in the system are restricted, see Def.~\ref{def:trans}, then
 it holds that the transition labels are of the form  $v=\link{\silent}{\silent}\dots\link{\silent}{\silent}$.\\
 Now,
by Definition~\ref{def:trans} and by Lemma~\ref{lem:struct}.1, all the  channels $r_j,p_j$, with
 $j \in [1,\dots,u]$, and $cxt$,
 %$cxt_h$, with $h \in [1, \dots, w]$,
  and all the annotated versions of 
 $s_i$, $s_o$ are restricted. Also, processes $\mathit{Cxt}$ always requires the 
 interaction with $P_s$ on either on channels $\widehat{s}_i$, $\widehat{s}_o$ or on channels 
 $\underline{s}_i$, $\underline{s}_o$.
 It derives that all the processes: $P_a$  (coding the behaviour of reaction $a \in A$), $P_s$ (coding the behaviour of entity $s \in S$), and $\mathit{Cxt}$ (coding the behaviour of the context regarding all the entities) have been involved in the transition.

@@

\item[(d)] 
 if $aj$ is not applicable,
the process $P_{aj}$ executes a code  capturing either the absence of one of its reactants (case 1), or the presence  of one of its inhibitors (case 2):
\begin{enumerate}
\item $P_{aj}\defeq \link{r_j}{\dots}\chainedlink{\overline{s}_i}{\noact}\chainedlink{\noact}{\overline{s}_o}\link{}{\dots} \chainedlink{r_{j+1}}{\noact}\chainedlink{\noact}{p_j}\link{}{\dots}\link{}{p_{j+1}}.P_{aj} $;
\item $P_{aj}\defeq \link{r_j}{\dots}\chainedlink{s_i}{\noact}\chainedlink{\noact}{s_o}\link{}{\dots} \chainedlink{r_{j+1}}{\noact}\chainedlink{\noact}{p_j}\link{}{\dots}\link{}{p_{j+1}} .P_{aj}$.
\end{enumerate}
\end{description}
%It is worth nothing that there could be other processes $P_a$ encoding  a reaction $a \in A$ that do not
%involve the entity $s$.\\
Now, we consider the structure of the process $\mathit{Cxt}^1$. 
By Definition~\ref{def:trans}, $Cxt^1$ is the unique process encoding the behaviour of the context regulating the supply of any entity.

\begin{description}
\item[(e)] 
The code of the process $Cxt^1$ that provides $s$ and not $e$ has the following structure: 
$$
\mathit{Cxt}^1 \defeq
\link{\mathit{cxt}}{\dots}
\chainedlink{\widehat{s}_i}{\noact}\chainedlink{\noact}{\widehat{s}_o}\link{}{\dots} 
\chainedlink{\underline{e}_i}{\noact}\chainedlink{\noact}{}\link{\underline{e}_o}{\dots} 
\chainend{p_{1}}. \mathit{Cxt}^{2} .
$$
\end{description}

>>>>

\lemmastruct*
\begin{proof}
  We prove the two items separately:
  \begin{enumerate}
\item by Definition~\ref{def:trans}, all the names that appear in the prefixes of any subprocess are in the set $\mathit{names}$ and thus restricted. 
They include all the reaction names $r_j$, all the production names $p_j$, all the entity names $s_i,s_o$, in all their decorated versions, and the name $\mathit{cxt}$. 
Therefore the chain $\upsilon$ must start and end with a $\silent$ action and cannot contain virtual links.
The only prefix that starts with $\silent$ is the one of the recursive init process $I$ (prefix $\link{\silent}{r_1}$) and the only prefixes that end with $\silent$ are those associated to reaction $a_u$ (as we have assumed that $p_{u+1} = \silent$, where $u$ is the number of reactions).
Then each prefix that starts with $r_j$ involves $p_j$ and $r_{j+1}$.
Thus all the prefixes associated with reactions must be concatenated and also the prefix associated with the context (remember that $r_{u+1} = \mathit{cxt}$), forming the backbone of the label.
Since the context processes is involved, then all entities processes are also involved.
Then, all the processes $I$, $P_a$, $P_s$ (or $\overline{P_s}$), and $\mathit{Cxt}_1$  must participate to each transition.
 \item for each reaction $aj \in A$, the c\CNA \ code of  $P_{aj}$ leaves one virtual link between two solid links of the types $\link{r_j}{\dots} \chainedlink{s_{i}}{\noact}\chainedlink{\noact}{s_{o}}\link{}{\dots}\link{}{r_{j+1}} {\dots}\link{p_j}{\dots}\link{}{p_{j+1}}$. Then, it derives that the process $P_{s}$, encoding the behaviour of entity $s$, can participate by filling the virtual link in the above transition by only offering one solid link of the form $\link{s_{i}}{s_{o}}$. In fact, there is no other way to generate a solid chain from $s_{i}$ to $s_{o}$.
 The same reasoning holds for the processes $\mathit{Cxt}_1$ and for all the decorated versions of $s_i,s_o$.
% $P_{s_1}$ can not participate with a link chain, as by juxtaposing  $\link{s_{1i}}{s_{1o}}$, not valid
 %link chains would be generated.
   \end{enumerate}
  \end{proof}

@@

 %\begin{proposition}(correctness 1)\\
 %\label{lem:struct}
%  Let ${\cal A} = (S, A)$ be a rs, and let  $\pi=(\gamma,\delta)$ be a $n$-step interactive process in $A$, with
% $\gamma = C_0,\dots,C_n$ and $\delta = D_0,\dots,D_n$.
%% We define $\pi' = (\gamma',\delta')$ with $\gamma' = C_0',\dots,C_{n-1}'$ and $\delta' = D_0',\dots,D_{n-1}'$ as $C_0' = C_1 \cup D_1$,  and
%% $C_i' = C_{i+1}$, $D_{i}' = D_{i+1}$ with $ 1 \leq i < n$.
%  Let   $P=[|{\cal A},\gamma|]$ be  its c\CNA~translation, and let $P'$ be such that $P \xrightarrow{\link{\silent}{\silent}}P'$.% then $P' = [|{\cal A},\gamma' |]$. 
%Then it holds that\\
% $P= \restrict{reacts,ctxs,ents} (\Pi_{a \in A}P_a| \Pi_{s \in S}CXT_s | \Pi_{s \in C_0}P_s| \Pi_{s \notin C_0}\overline{P}_s)$\\
% $P'= \restrict{reacts,ctxs,ents} (\Pi_{a \in A}P_a| \Pi_{s \in S}CXT_s | \Pi_{s \in C_1 \cup D_1}P_s| \Pi_{s \notin C_1 \cup D_1}\overline{P}_s)$
 %\end{proposition}
 \begin{proof}
 First, we note that all the channels in the system are restricted, see Def.~\ref{def:trans}, then
 it holds that the transition labels are of the form  $v=\link{\silent}{\silent}\dots\link{\silent}{\silent}$.\\
 Now,
by Definition~\ref{def:trans} and by Lemma~\ref{lem:struct}.1, all the  channels $r_j,p_j$, with
 $j \in [1,\dots,u]$, and $cxt$,
 %$cxt_h$, with $h \in [1, \dots, w]$,
  and all the annotated versions of 
 $s_i$, $s_o$ are restricted. Also, processes $\mathit{Cxt}_1$ always requires the 
 interaction with $P_s$ on either on channels $\widehat{s}_i$, $\widehat{s}_o$ or on channels 
 $\underline{s}_i$, $\underline{s}_o$.
 It derives that all the processes: $P_a$  (coding the behaviour of reaction $a \in A$), $P_s$ (coding the behaviour of entity $s \in S$), and $\mathit{Cxt}_1$ (coding the behaviour of the context regarding all the entities) have been involved in the transition.

@@

\item[(d)] 
 if $aj$ is not applicable,
the process $P_{aj}$ executes a code  capturing either the absence of one of its reactants (case 1), or the presence  of one of its inhibitors (case 2):
\begin{enumerate}
\item $P_{aj}\defeq \link{r_j}{\dots}\chainedlink{\overline{s}_i}{\noact}\chainedlink{\noact}{\overline{s}_o}\link{}{\dots} \chainedlink{r_{j+1}}{\noact}\chainedlink{\noact}{p_j}\link{}{\dots}\link{}{p_{j+1}}.P_{aj} $;
\item $P_{aj}\defeq \link{r_j}{\dots}\chainedlink{s_i}{\noact}\chainedlink{\noact}{s_o}\link{}{\dots} \chainedlink{r_{j+1}}{\noact}\chainedlink{\noact}{p_j}\link{}{\dots}\link{}{p_{j+1}} .P_{aj}$.
\end{enumerate}
\end{description}
%It is worth nothing that there could be other processes $P_a$ encoding  a reaction $a \in A$ that do not
%involve the entity $s$.\\
Now, we consider the structure of the process $\mathit{Cxt}_1$. 
By Definition~\ref{def:trans}, $Cxt_1$ is the unique process encoding the behaviour of the context regulating the supply of any entity.

\begin{description}
\item[(e)] 
The code of the process $Cxt_1$ that provides $s$ and not $e$ has the following structure: 
$$
\mathit{Cxt}_1 \defeq
\link{\mathit{cxt}}{\dots}
\chainedlink{\widehat{s}_i}{\noact}\chainedlink{\noact}{\widehat{s}_o}\link{}{\dots} 
\chainedlink{\underline{e}_i}{\noact}\chainedlink{\noact}{}\link{\underline{e}_o}{\dots} 
\chainend{p_{1}}. \mathit{Cxt}_{2} .
$$
\end{description}
